The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2014-07-04 article.tex

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
    \rowcolors{1}{}{lightgray}
    \par
    \mbox{
    \begin{tabular}{lcclrc}
    \toprule
                             & Bit version  & Count version & CDK version & Default Size & References \\
  CirkularFingerprinter      & $\checkmark$ & ?             & ?           & ?            & [pending?] \\
  EStateFingerprinter        & $\checkmark$ &               & 1.2.0       & $79$         & \cite{Hall1995}\\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         &              & \\
  Fingerprinter              & $\checkmark$ &               & 1.0         &              & \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         &              & \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       &              & \\
  KlekotaRothFingerprinter   & $\checkmark$ &               & 1.4.6       & $4\,860$     & \cite{Klekota2008}\\
  LingoFingerprinter         & $\checkmark$ &               & 1.6.0 ?     &              & \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       &              & \\
  PubchemFingerprinter       & $\checkmark$ &               & 1.4.0       &              & \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     &              & \\
  SignatureFingerprinter     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$     & [pending] \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         &              & \\
  \bottomrule
    \end{tabular}}

>>>>

\newpage

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{lcclcc}
    \toprule
                             & Bit version  & Count version & CDK version & Default Size    & References \\
  CirkularFingerprinter      & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CirkularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded}
                                                                                            & \cite{rogers2010extended, pending?} \\
  EStateFingerprinter        & $\checkmark$ &               & 1.2.0       & $79$            & \cite{Hall1995} \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        & \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        & \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        & \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        & \\
  KlekotaRothFingerprinter   & $\checkmark$ &               & 1.4.6       & $4\,860$        & \cite{Klekota2008} \\
  LingoFingerprinter         & $\checkmark$ &               & 1.6.0 ?     & NA%
\footnote[2]{The Lingofingerprinter does not have a default size}               
                                                                                            & \cite{vidal2005lingo} \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           & \\
  PubchemFingerprinter       & $\checkmark$ &               & 1.4.0       & $881$           & \cite{pubchemFP} \\
  ShortestPathFingerprinter  & $\checkmark$ &               & 1.6.0 ?     & $1\,024$        & \\
  SignatureFingerprinter     & $\checkmark$ & $\checkmark$  & 1.6.0 ?     & $2^{32}$        & [pending] \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           & \\
  \bottomrule
    \end{tabular}
    \end{minipage}
